---
title: "README"
author: "Julian Trachsel"
date: "5/10/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Install gifrop

Make sure you have some kinda of conda installation completed.  I like miniconda.  
https://www.docs.conda.io/en/latest/miniconda.html  
  
Once you have miniconda install gifrop.  


From the command line:  
```{bash, eval=FALSE}
conda create -n gifrop
conda activate gifrop
conda install -c conda-forge -c bioconda -c defaults gifrop
```


# Clone test repo

```{bash, eval=FALSE}
git clone https://www.github.com/jtrachsel/gifrop_examples.git  
cd gifrop_examples

```


# First Test



* Two strains of Salmonella enterica  
  + LT2: famous reference strain  
  + USDA15WA-1: Isolate under investigation in the Bearson Lab

Two genomic islands of interest here.  80kb metal tolerance island (SGI4), 28kb multidrug resist module.  
  
For this example I have already annotated the genomes with prokka and generated the pangenome with Roary.  
```{bash}
cd test1

cd pan
pan_pipe --prokka_args '--cpus 4 --proteins LT2.gbk' --roary_args '-p 8' --gifrop_args '--threads 8'

cd gifrop_out

```


```{r}

```






